### 2008-03-04 SAiP/Module1/H3/doc/softwarearchitecture.tex
Updating with diagram

\subsubsection{Elements}
Based on the present decomposition the elements that are know the layers, where each layer is an element as described below.
\begin{itemize}
    \item[Clients] The clients access the server inorder to perform some action
    \item[Server] The server is accessed by the clients and when needed access the database via its Fa\c cade pattern.
    \item[Database] The database exposes its interface to the server via a Fa\c cade pattern.
\end{itemize}
\fixme{Insert element (class) diagram for the above}

\subsubsection{Relations}

>>>>

\subsubsection{Elements}
Based on the present decomposition the elements that are know the layers, where each layer is an element as described below.
\begin{itemize}
    \item[Clients] The clients access the server in order to perform some action.
    \item[Server] The server is accessed by the clients and when needed access the database via its Fa\c cade pattern.
    \item[Database] The database exposes its interface to the server via a Fa\c cade pattern.
\end{itemize}
The above is quickly sketched in the box-and-line drawing below, where the layering may also be seen.
\begin{figure}[!htb]
\centerline{\epsfig{figure=figures/module_view,scale=1.0 }}
\caption{Module-View overview}
\label{fig:module_view}
\end{figure}
\clearpage

\subsubsection{Relations}
The figure xx shows some of the relations, namely the statical, yet it is also important to know the dynamical behaviour.
